An open reproducible framework for the study of the iterated prisoner's dilemma

### 2016-02-03 tex/paper.tex
Adding a conclusion.

>>>>

This paper has presented a game theoretic software package that aims to address
reproducibility of research in to the iterated prisoner's dilemma. Through the
very nature of the development of this library, all open research and
development, it has not only acquired a large number of strategies (120) but
also already discovered various insights that will lead to further publications.

The capabilities of the library mentioned above are not at all comprehensive, a
list of the current abilities include:

\begin{itemize}
    \item Noisy tournaments;
    \item Ecological analysis of tournaments;
    \item Morality metrics based on \cite{Singer-Clark2014};
    \item Transformation of strategies (in effect giving an infinite number of
        strategies);
    \item Classification of strategies according to multiple dimensions.
\end{itemize}

These capabilities are constantly being updated. Some immediate further work
includes allowing for tournaments of probabilistic length as well as further
implementation of known strategies

The ability to readily have available a large number of strategies makes this
tool an excellent and obvious example of the benefits of open research which
should positively impact the game theoretic community.
